% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.
%To get the shading to work:
%DVI->PS->PDF
%On command prompt Try (where 'resume' is name whatever this is saved as):
%latex resume.tex
%dvips -Ppdf -t letter resume.dvi
%ps2pdf resume.ps

\documentclass[letterpaper, 11pt]{article}

%-----------------------------------------------------------
%Margin setup

%\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{10in}
\setlength{\topmargin}{-0.54in}
\setlength{\textwidth}{7.5in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\evensidemargin}{-0.5in}
%-----------------------------------------------------------
%\usepackage{fullpage}
\usepackage{shading}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubheadinga}[2]{
\begin{tabular*}{7.11in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
\end{tabular*}}

\newcommand{\ressubheadingb}[2]{
\begin{tabular*}{7.11in}{l@{\extracolsep{\fill}}r}
		\textit{#1} & \textit{#2} \\
\end{tabular*}\vspace{-6pt}}

%-----------------------------------------------------------


\begin{document}
\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Daksh Jotwani} \vspace{1pt}\\
dakshjotwani@gmail.com & www.dakshjotwani.com\\
(415) 866-9794 & github.com/dakshjotwani\\
\end{tabular*}
%\bigskip
\vspace{-0.15in}
%\textbf{Objective:} Not sure if needed 
\resheading{Education}
\vspace{-0.235in}
\begin{itemize}

\item
	\ressubheadinga{Purdue University}{West Lafayette, IN}
	\ressubheadingb{B.S. Computer Science, Mathematics}{August 2016 - Present}
	\begin{itemize}
		\resitem{GPA: \textbf{3.94/4.00}, Expected Graduation Date: \textbf{May 2020}}
		\resitem{Coursework: Deep Learning, Data Structures, Algorithms, Systems Programming, Linear Algebra}
	\end{itemize}

\end{itemize}

\vspace{-0.23in}
\resheading{Work Experience}
\vspace{-0.235in}

\begin{itemize}
\item
	\ressubheadinga{Tesla}{Palo Alto, CA}
	\ressubheadingb{Software Engineer Intern}{September 2019 - Present}
	\begin{itemize}
        \resitem{Deployed a user-space out of memory killer for Tesla's Powerwall and industrial energy products.}
        \resitem{Building an OTA update system for Tesla's industrial energy systems to Tesla's proprietary OS.}
	\end{itemize}
\end{itemize}

\begin{itemize}
\item
	\ressubheadinga{Flipkart Myntra}{Bangalore, India}
	\ressubheadingb{Data Scientist Intern}{May 2019 - August 2019}
	\begin{itemize}
            \resitem{Trained and deployed a face recognition-based authentication service to allow registered Flipkart customers to enter their unmanned stores.}
            \resitem{Prototyped person reidentification (ReID) and human action detection models to automatically generate shopping cart receipts for Flipkart and Myntra's offline stores.}
	\end{itemize}
\end{itemize}

\begin{itemize}
\item
    \ressubheadinga{Purdue University}{West Lafayette, IN}
    \ressubheadingb{Undergraduate Teaching/Research Assistant}{August 2018 - May 2019}
    \begin{itemize}
        \resitem{Held and graded labs for a \emph{Systems Programming} class that covers operating systems fundamentals.}
            \resitem{Analyzed the performance impact of speculative region search for data-points in overlapping regions of an R-tree. Based on \textit{The Case For Learned Index Structures} (arxiv.org/abs/1712.01208).}
        \resitem{Constructed logistic regression and neural network models to speculate traversal routes of an R-tree.}
    \end{itemize}
\end{itemize}

\begin{itemize}
\item
	\ressubheadinga{Myntra}{Bangalore, India}
	\ressubheadingb{Software Engineering Intern}{May 2018 - August 2018}
	\begin{itemize}
		\resitem{Applied computer vision techniques to monitor store traffic, analyze age/gender demographics, identify returning customers, and detect visual customer satisfaction.}
		\resitem{Developed a system where computer vision-based inferences from store cameras are broadcast to store devices to provide personalized services such as product/size recommendations to customers.}
	\end{itemize}
\end{itemize}

\vspace{-0.16in}
\resheading{Projects and Contributions}
\vspace{-0.235in}

\begin{itemize}
\item
    \ressubheadinga{(Contribution) PyTorch}{\emph{June 2019 - July 2019}}
    \vspace{-0.25in}
    \begin{itemize}
            \resitem{Built a class-balanced dataset batch sampler (\texttt{PKSampler}) and an online triplet mining loss function (\texttt{TripletMarginLoss}) for PyTorch's torchvision module to tackle similarity learning problems.}
            \resitem{Wrote training/evaluation reference scripts to showcase torchvision's similarity learning tools.}
    \end{itemize}

\item
    \ressubheadinga{GTAi: Self Driving Car in GTA 5}{\emph{March 2019 - Present}}
    \vspace{-0.25in}
    \begin{itemize}
            %\resitem{Applied imitation learning to make a car drive itself in \emph{GTA V}.}
            \resitem{Built a data-collection pipeline to map frames to controller inputs and load them for model training.}
            \resitem{Modelled a neural network architecture to output controls for a given frame using ResNet50 as a feature extractor, followed by a LSTM to infer temporal information from a sequence of frames.}
    \end{itemize}

\item
    \ressubheadinga{PayShare}{\emph{May 2018 - September 2018}}
    \vspace{-0.25in}
    \begin{itemize}
        \resitem{Developed a web application using React and Firebase to split expenses among a group of people.}
        \resitem{Applied Tesseract OCR to scan receipts and generate a list of items for users to select and split.}
    \end{itemize}

%\item
%    \ressubheadinga{SmartPass}{\emph{October 2016}}
%    \vspace{-0.25in}
%    \begin{itemize}
%        \resitem{Built an event-ticketing system which authorizes people using face/voice recognition.}
%        \resitem{Deployed a server to provide face recognition services for iOS devices to identify people at events.}
%    \end{itemize}
\end{itemize}

\vspace{-0.16in}
\resheading{Skills}
\vspace{-0.10in}

\textbf{Languages:} Python, JavaScript, C/C++, Java, Go. \textbf{Frameworks:} PyTorch, TensorFlow, OpenCV, Git, React.

\end{document}
